### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@3c7c22bca70e6bc71bb73bc363c08415f51deca3 🚀

Assuming a no-skill unbiased classifier (\emph{i.e.}
\(\mathbf{C}=\matbf{M}\)), the accuracy is \(\rho^2 + (1-\rho)^2\), the
balanced accuracy is \(0.5\), Youden's J is \(0\), and \(F_1=\rho\). In
other words, given a connectance \(\rho = 0.05\), we expect that a
classifier guessing at random would still achieve an accuracy of
\(0.905\); for a connectance of \(\rho = 0.01\), this accuracy
\emph{increases} to over \(0.98\). In other words, networks with fewer
interactions have inherently higher accuracy, because it is easy to
predict the overwheling majority of non-interactions right.

@@

\hypertarget{effect-of-training-set-on-performance}{%
\subsection{Effect of training set on
performance}\label{effect-of-training-set-on-performance}}

>>>>

Assuming a no-skill unbiased classifier (\emph{i.e.}
\(\mathbf{C}=\mathbf{M}\)), the accuracy is \(\rho^2 + (1-\rho)^2\), the
balanced accuracy is \(0.5\), Youden's J is \(0\), and \(F_1=\rho\). In
other words, given a connectance \(\rho = 0.05\), we expect that a
classifier guessing at random would still achieve an accuracy of
\(0.905\); for a connectance of \(\rho = 0.01\), this accuracy
\emph{increases} to over \(0.98\). In other words, networks with fewer
interactions have inherently higher accuracy, because it is easy to
predict the overwheling majority of non-interactions right.

@@

\hypertarget{effect-of-training-set-bias-on-performance}{%
\subsection{Effect of training set bias on
performance}\label{effect-of-training-set-bias-on-performance}}
